A Motion Capture and Imitation Learning-based Approach to Robot Control

### 2022-06-28 tex-arxiv/article.tex
conclusions fix + acknowledgments

In contrast to some previous work that has explored motion capture in imitation learning, we place a greater emphasis on using general-purpose machine learning methods -- artificial neural networks -- to generate the trajectories at inference, as opposed to simple neighbor methods \citep{jha2017imitation} or highly domain-specific approaches grounded in the use of dynamic motion primitives \citep{vuga2013mocap}. To more objectively evaluate the performance of the policies obtained with various hyperparameters and on different data sets, a series of quantitative metrics are proposed in this paper. In general, it can be said that, according to these, recurrent networks operating on complete state histories outperform simple deep neural networks operating in a Markovian mode -- which is perhaps unsurprising, given the recent successes achieved in applying general-purpose sequence-to-sequence learning methods to the imitation learning domain \citep{reed2022generalist}. As our model precision comparisons rely on indirect estimates rather than empirical data, it is hard to make a direct comparison with state-of-the-art performers in throwing tasks such as \citep{zeng2020tossingbot} -- but it should be noted that they use learning at a higher level -- outputting parameters that describe each throw -- and do not use model outputs to generate Cartesian motion plans directly like we do. This makes their entire approach inherently more coupled to a single type of task than ours.

@@

>>>>

In contrast to some previous work that has explored motion capture in imitation learning, we place a greater emphasis on using general-purpose machine learning methods -- artificial neural networks -- to generate the trajectories at inference, as opposed to simple neighbor methods \citep{jha2017imitation} or highly domain-specific approaches grounded in the use of dynamic motion primitives \citep{vuga2013mocap}. To more objectively evaluate the performance of the policies obtained with various hyperparameters and on different data sets, a series of quantitative metrics are proposed in this paper. In general, it can be said that, according to these, recurrent networks operating on complete state histories outperform simple deep neural networks operating in a Markovian mode -- which is perhaps unsurprising, given the recent successes achieved in applying general-purpose sequence-to-sequence learning methods to the imitation learning domain \citep{reed2022generalist}. As our model precision comparisons rely on indirect estimates rather than empirical data, it is hard to make a direct comparison with state-of-the-art performers in throwing tasks such as \citep{zeng2020tossingbot} -- but it should be noted that they use learning at a higher level -- outputting parameters that describe each throw -- and do not use model outputs to generate Cartesian motion plans directly as proposed here. This makes their entire approach inherently more coupled to a single type of task than ours.

@@

\paragraph{Acknowledgements.} This work was funded by the Electronic Components and Systems For European Leadership Joint Undertaking (ECSEL JU) in collaboration with the European Union’s H2020 Framework Programme under grant agreement No 826600.
